RCloud: Integrated Visualization, Analysis, Development, and Deployment

### 2015-01-02 paper.tex
new teaser skeleton

\title{RCloud: Integrating Exploratory Visualization, Analysis and Deployment}
%% \title{RCloud: DevOps for Visual Analysis and Data Science}

@@

%% Uncomment below to include a teaser figure.
\teaser{
  \centering
  \includegraphics[width=.28\linewidth]{fig/screenshots/wdcplotsmall.jpg}
  %% \includegraphics[width=.9\linewidth]{figs/teaser.jpg}
  \hspace{1em}
  \includegraphics[width=.6\linewidth]{fig/casestudy1/casestudy1.graffle/image8.png}
  % \vspace{-.5em}
  \caption{RCloud provides infrastructure for data science teams so
    that R \emph{hackers} and \emph{scripters}~\cite{Kandel:2012:EDA} can target modern
    interactive visualization technologies such as
    D3~\cite{Bostock:2011:DDD}, dc.js~\cite{DCJS:2014:DC} and
    Crossfilter~\cite{Square:2014:CFM} (left), while at the same time
    enabling seamless deployment and dashboarding for
    \emph{application users} (right).
    \carlos{Replace this with something using either a Shiny demo or in-process nanocubes?}
  }
% \vspace{-.5em}
}

>>>>

\title{RCloud: Integrated Visualization, Analysis, Development, and Deployment}

@@

%% Uncomment below to include a teaser figure.
\teaser{
  \centering
  \includegraphics[width=.95\linewidth]{fig/teaser/teaser.pdf}
  % \vspace{-.5em}
  \caption{
    \carlos{Come up with caption for this. The story is: hackers/scripters work in the middle (and bottom-right), rest of organization has automatic access to their work on left and top-right.}
  }
% \vspace{-.5em}
}
